Plant Modeling for an Autonomous Vehicle

### 2022-04-19 finalReportPres.tex
finalReportPres.tex updates
I added pictures of the simulink neural network models to the presentation
Presentation and Poster Updates
I added the new subsystem block diagrams to the presentation and made some edits to the poster

\usepackage{pgfgantt}
\usepackage{todonotes}
\usepackage{media9}
% \usepackage{subfigure}
\usepackage{booktabs,array}
\usepackage[font=tiny,labelfont=bf]{caption}
\usepackage{tabulary}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{arydshln}
\usepackage{rotating}
\usepackage{amsmath,amssymb,amsfonts,bm}

@@

\begin{frame}{System Architecture}{}
%  \missingfigure{Place the overall vehicle picture from the report that shows different subsystems  }
\begin{figure}
				\centering
				\includegraphics[height=3.5cm]{figs/inkscape/carSystemModelOutline}
				%\caption{}
				\label{fig:carSystemSubsystem}
        \end{figure}
%	\begin{block}{System Architecture}
%    The overall system architecture of this project consists of six subsystems: 
%    \begin{itemize}
%        \item Steering
%        \item Acceleration
%        \item Brake %Model
%        \item Shift %Model
%        \item Speed %Model
%        \item Speed control %Model
%      \end{itemize} 
%  \end{block}
\end{frame}

@@

\begin{frame}{System Architecture}{Subsystems}
	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/steeringModelArchitecture}\quad%
	\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Steering System 			\item Brake System \item Acceleration System \end{enumerate} \end{minipage}\\[1em]
	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/brakeModelArchitecture}\quad%
	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/accelerationModelArchitecture}
\end{frame}

\begin{frame}{System Architecture}{Subsystems}
	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/shiftModelArchitecture}\quad%
	\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Shift System \item 		Speed Control System \item Speed System \end{enumerate} \end{minipage}\\[1em]
	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedControlModelArchitecture}\quad%
	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedModelArchitecture}
\end{frame}

@@

  \todo[inline]{Where are the detailed simulink block diagram for each subsystem?}
\end{frame}

>>>>

\usepackage{pgfgantt}
\usepackage{todonotes}
\usepackage{media9}
% \usepackage{subfigure}
\usepackage{booktabs,array}
\usepackage[font=tiny,labelfont=bf]{caption}
\usepackage{tabulary}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{arydshln}
\usepackage{rotating}
\usepackage{amsmath,amssymb,amsfonts,bm}
\usepackage{tikz}

@@

\begin{frame}{System Architecture}{}
%  \missingfigure{Place the overall vehicle picture from the report that shows different subsystems  }
\begin{figure}
				\centering
				\includegraphics[height=3.5cm]{figs/inkscape/carSystemModelOutline}
				\label{fig:carSystemSubsystem}
				\caption{Lexus Vehicle with Subsystems}
        \end{figure}
%	\begin{block}{System Architecture}
%    The overall system architecture of this project consists of six subsystems: 
%    \begin{itemize}
%        \item Steering
%        \item Acceleration
%        \item Brake %Model
%        \item Shift %Model
%        \item Speed %Model
%        \item Speed control %Model
%      \end{itemize} 
%  \end{block}
\end{frame}

@@

\begin{frame}{System Architecture}{Subsystems}

\begin{figure}
  \centering
  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=0.75 cm]
    \tikzstyle{sum} = [draw, circle,fill=orange!15]
    % place nodes
    \node[sum](sum){$\sum$};
    \node[block,right of=sum,node distance=2 cm, text width=1.25cm,text centered](steeringController){Steering controller};
    \node[block,right of=steeringController,node distance=2.25 cm, text width=1.3cm,text centered](steeringSubsystem){Steering subsystem};

    % Connections
    \draw[stealth-,thick]
    (sum.west)--node[very near start,above]{$+$}++(-0.5,0)node[above]{$\theta^{\text{ref}}$};
    \draw[-stealth,thick]
    (sum.east)--node[midway,above]{Error}(steeringController);
    \draw[-stealth,thick]
    (steeringController.15)--node[midway,above]{$v_A$}(steeringSubsystem.165);
    \draw[-stealth,thick]
    (steeringController.-15)--node[midway,above]{$v_B$}(steeringSubsystem.-165);
    \draw[-stealth,thick]
    (steeringSubsystem.east) --coordinate (tt) ++(0.5,0)node[above]{$\theta(t)$};
    \fill
    ($(steeringSubsystem.east)+(0.25,0)$) circle [radius=2pt];
    \draw[-stealth,thick]
    (tt) -- ++(0,-0.75) -|(sum.south)node[pos=0.9,left]{$-$};

  \end{tikzpicture}
  % \captionsetup{justification=centering, margin=3cm}

  % \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
  \caption{Steering subsystem block diagram.}
  \label{fig:steeringModelBlockDiagram}
\end{figure}

\begin{figure}
    \centering
  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2.0 cm]
    % place nodes
    \node[block,text width=1.25cm,text centered](brakeSubsystem){Brake subsystem};

    % Connections
    \draw[stealth-,thick]
    (brakeSubsystem.140)--node[pos=0.65,above]{Pressure voltages}++(-2.0,0);
    \draw[stealth-,thick]
    (brakeSubsystem.180)--node[pos=0.65,above]{Stroke voltages}++(-2.0,0);
    \draw[stealth-,thick]
    (brakeSubsystem.-140)--node[pos=0.65,above]{On/Off switch}++(-2.0,0);
    \draw[-stealth,thick]
    (brakeSubsystem.30)--node[pos=0.5,above]{Pedal position}++(2.2,0);
    \draw[-stealth,thick]
    (brakeSubsystem.-30)--node[pos=0.5,below]{Brake pressed}++(2.2,0);

  \end{tikzpicture}
    % \captionsetup{justification=centering, margin=3cm}
    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
    \caption{Brake subsystem block diagram}
    \label{fig:brakeModelArchitecture}
\end{figure}

%	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/steeringModelArchitecture}\quad%
%	\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Steering System 			\item Brake System \item Acceleration System \end{enumerate} \end{minipage}\\[1em]
%	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/brakeModelArchitecture}\quad%
%	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/accelerationModelArchitecture}
\end{frame}
%
\begin{frame}{System Architecture}{Subsystems}

\begin{figure}[htbp]
    \centering
  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.75cm,text centered](accelSubsystem){Acceleration subsystem};
    % Connections
    \draw[stealth-,thick]
    (accelSubsystem.180)--node[very near end,above]{Acceleration pedal voltages}++(-2.5,0);
    \draw[-stealth,thick]
    (accelSubsystem.0)--node[very near end,above]{Acceleration pedal position}++(2.5,0);
  \end{tikzpicture}
    \caption{Acceleration subsystem block diagram}
    \label{fig:accelModelArchitecture}
 \end{figure}

 \begin{figure}
    \centering
  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};

    % Connections
    \draw[stealth-,thick]
    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-1.9,0);
    \draw[-stealth,thick]
    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(1.9,0);

  \end{tikzpicture}
    \caption{Shift subsystem block diagram}
    \label{fig:shiftModelArchitecture}
 \end{figure}

%	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/shiftModelArchitecture}\quad%
%	\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Shift System \item 		Speed Control System \item Speed System \end{enumerate} \end{minipage}\\[1em]
%	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedControlModelArchitecture}\quad%
%	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedModelArchitecture}
\end{frame}

\begin{frame}{System Architecture}{Subsystems}
\begin{figure}[htbp]
    \centering
  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2 cm]
    % place nodes
    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};

    % Connections
    \draw[stealth-,thick]
    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-2.5,0);
    \draw[stealth-,thick]
    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-2.5,0);
    \draw[stealth-,thick]
    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-2.5,0);
    \draw[-stealth,thick]
    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(1.9,0);

  \end{tikzpicture}
    % \captionsetup{justification=centering, margin=3cm}
    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
    \caption{Speed subsystem block diagram}
    \label{fig:speedModelArchitecture}
\end{figure}

\begin{figure}[htbp]
    \centering
  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};

    % Connections
    \draw[stealth-,thick]
    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-1.9,0);
    \draw[-stealth,thick]
    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(1.9,0);

  \end{tikzpicture}
    \caption{Speed Control subsystem block diagram}
    \label{fig:speedControlModelArchitecture}
 \end{figure}

@@

%  \todo[inline]{Where are the detailed simulink block diagram for each subsystem?}
	\begin{figure}
		\centering \includegraphics[width=.35\linewidth]{figs/img/steeringNeuralNetworkDetailedSystem}\quad%
		\caption{Steering Neural Network Simulink Model Subsystem}
		\centering \begin{minipage}[b][0.35\textheight][c]{.35\linewidth} 
%		\begin{itemize} \item HIL Bench 						
%		\item Measuring output voltages to confirm results \end{itemize} 
		\end{minipage}\\[1em]
		\centering \includegraphics[width=.35\linewidth]{figs/img/accelNeuralNetworkDetailedSystem}\quad%
		\caption{Acceleration Neural Network Simulink Model Subsystem}
		\centering \includegraphics[,width=.35\linewidth]{figs/img/brakeNeuralNetworkDetailedSystem}
		\caption{Brake Neural Network Simulink Model Subsystem}
	\end{figure}
\end{frame}

### 2022-04-19 poster.tex
Presentation and Poster Updates
I added the new subsystem block diagrams to the presentation and made some edits to the poster

\begin{figure}
    \centering
        \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};

    % Connections
    \draw[stealth-,thick]
    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-4.0,0);
    \draw[-stealth,thick]
    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(4.0,0);

  \end{tikzpicture}
    \caption{Speed Control subsystem block diagram}
    \label{fig:speedControlModelArchitecture}

\end{figure}

\begin{figure}
    \centering
  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=2 cm]
    % place nodes
    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};

    % Connections
    \draw[stealth-,thick]
    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-5.0,0);
    \draw[stealth-,thick]
    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-5.0,0);
    \draw[stealth-,thick]
    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-5.0,0);
    \draw[-stealth,thick]
    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(5.0,0);

  \end{tikzpicture}
    % \captionsetup{justification=centering, margin=3cm}
    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
    \caption{ Speed subsystem block diagram}
    \label{fig:speedModelArchitecture}
\end{figure}

\begin{figure}
    \centering
\begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};

    % Connections
    \draw[stealth-,thick]
    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-4.5,0);
    \draw[-stealth,thick]
    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(4.5,0);

  \end{tikzpicture}
    \caption{Shift subsystem block diagram}
    \label{fig:shiftModelArchitecture}
\end{figure}

@@

>>>>

%\begin{figure}
%    \centering
%        \begin{tikzpicture}
%    \tikzstyle{every node} = [font=\footnotesize]
%    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
%    % place nodes
%    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};
%
%    % Connections
%    \draw[stealth-,thick]
%    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-4.0,0);
%    \draw[-stealth,thick]
%    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(4.0,0);
%    
%  \end{tikzpicture}
%    \caption{Speed Control subsystem block diagram}
%    \label{fig:speedControlModelArchitecture}
%
%\end{figure}
%
%
%\begin{figure}
%    \centering
%  \begin{tikzpicture}
%    \tikzstyle{every node} = [font=\footnotesize]
%    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=2 cm]
%    % place nodes
%    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};
%
%    % Connections
%    \draw[stealth-,thick]
%    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-5.0,0);
%    \draw[stealth-,thick]
%    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-5.0,0);
%    \draw[stealth-,thick]
%    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-5.0,0);
%    \draw[-stealth,thick]
%    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(5.0,0);
%    
%  \end{tikzpicture}
%    % \captionsetup{justification=centering, margin=3cm}
%    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
%    \caption{ Speed subsystem block diagram}
%    \label{fig:speedModelArchitecture}
%\end{figure}

%\begin{figure}
%    \centering
%\begin{tikzpicture}
%    \tikzstyle{every node} = [font=\footnotesize]
%    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
%    % place nodes
%    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};
%
%    % Connections
%    \draw[stealth-,thick]
%    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-4.5,0);
%    \draw[-stealth,thick]
%    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(4.5,0);
%    
%  \end{tikzpicture}
%    \caption{Shift subsystem block diagram}
%    \label{fig:shiftModelArchitecture}
%\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.48\linewidth]{figs/inkscape/carSystemModelOutline}
	\caption{Lexus vehicle with subsystems}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.48\linewidth]{figs/img/picturesVisitToAStuff/visitors1-20211007}
	\caption{AutonomouStuff Lexus RX450H vehicle}
\end{figure}
